Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-08-07 ms.tex
minor revisions after soliciting comments

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and DIRBE/\IRAS~100$\mu$m emission with a 
single-MBB spectrum. Here we investigate the FDS99 two-component dust emission 
model as an alernative parametrization for the dust spectral energy 
distribution (SED) composed  of \PLANCK High Frequency Instrument (HFI), DIRBE 
and \IRAS~data. In doing so, we obtain maps of dust temperature and optical 
depth, both at $6.1'$ resolution. Because we employ a model that has been 
validated with FIRAS data down to submillimeter (submm) wavelengths, we expect 
our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a valuable cross-check for extinction 
estimates based directly upon optical observations of stars 
\citep[e.g.][]{schlafly14} and as a baseline for next-generation dust 
extinction maps incorporating high-resolution, full-sky infrared data sets such
as \WISE~\citep{wright10, meisner14} and \AKARI.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
low-resolution fits described in $\S$\ref{sec:lores}. Red coloring masks pixels
with appreciable molecular emission, as defined in $\S$\ref{sec:mole}. Such 
pixels should not be trusted in this analysis, which is sensitive to the SED 
shape at low frequencies affected by CO line emission. Variations in $f_1$
along the ecliptic plane are spurious results of imperfect zodiacal light
subtractions. However, interesting astrophysical variations of $f_1$ 
are evident, particularly the trend of increasing $f_1$ with decreasing
Galactic latitude, the relatively low $f_1$ values in the Polaris flare region,
and the clouds with relatively high $f_1$ near the north Galactic pole.}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. In both the top 
left and top right plots, the bending of the reddening residuals as a function 
of $E(B-V)_{SFD}$ seen in Figure \ref{fig:resid} has been eliminated. Further, 
the two-component reddening residual temperature dependence (bottom left) has 
been significantly reduced relative to the corresponding trend shown in Figure 
\ref{fig:resid}.}
\end{center}
\end{figure*}

>>>>

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and DIRBE/\IRAS~100$\mu$m emission with a 
single-MBB spectrum. Here we investigate the FDS99 two-component dust emission 
model as an alernative parametrization for the dust spectral energy 
distribution (SED) composed  of \PLANCK~High Frequency Instrument (HFI), DIRBE 
and \IRAS~data. In doing so, we obtain maps of dust temperature and optical 
depth, both at $6.1'$ resolution. Because we employ a model that has been 
validated with FIRAS data down to submillimeter (submm) wavelengths, we expect 
our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a valuable cross-check for extinction 
estimates based directly upon optical observations of stars 
\citep[e.g.][]{schlafly14} and as a baseline for next-generation dust 
extinction maps incorporating high-resolution, full-sky infrared data sets such
as \WISE~\citep{wright10, meisner14} and \AKARI.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM full-sky map of $f_1$ derived from our
low-resolution fits described in $\S$\ref{sec:lores}. Red coloring masks pixels
with appreciable molecular emission, as defined in $\S$\ref{sec:mole}. Such 
pixels should not be trusted in this analysis, which is sensitive to the SED 
shape at low frequencies affected by CO line emission. Variations in $f_1$
along the ecliptic plane are spurious results of imperfect zodiacal light
subtractions. However, interesting astrophysical variations of $f_1$ 
are evident, particularly the trend of increasing $f_1$ with decreasing
Galactic latitude, the relatively low $f_1$ values in the Polaris flare region,
and the clouds with relatively high $f_1$ near the north Galactic pole.}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but restricting 
to high ecliptic latitude, $|\beta|>20^{\circ}$. In both the top left and top 
right plots, the bending of the reddening residuals as a function of 
$E(B-V)_{SFD}$ seen in Figure \ref{fig:resid} has been eliminated. Further, the
two-component reddening residual temperature dependence (bottom left) has been 
significantly reduced relative to the corresponding trend shown in Figure 
\ref{fig:resid}. For $E(B-V)_{SFD}$$\gtrsim$0.3 mag, the top row plots appear 
noisy because there are an insufficient number of remaining SSPP points of 
comparison.}
\end{center}
\end{figure*}
